\newpage
\section{Theory of the Fourier Transform of the Fast Rotation Signal}

\subsection{Mathematical Preliminaries}

\begin{definition}[Fourier's transform and inverse transform]
Given a function $f$, its Fourier transform is \[\hat{f}(x)=\frac{1}{\sqrt{2\pi}}\int^{\infty}_{-\infty}f(t)e^{ixt}dt\] and its inverse Fourier transform is \[\tilde{f}(x)=\frac{1}{\sqrt{2\pi}}\int^{\infty}_{-\infty}f(t)e^{-ixt}dt\] If $f$ is absolutely integrable, then the Fourier transforms of $f$ always exist. It is easy to check that $f=\tilde{\hat{f}}=\hat{\tilde{f}}$.
\end{definition}

\begin{theorem}
For any piecewise continuous, piecewise differentiable, and absolutely integrable function $f$, the following equality holds: \[f(x)=\frac{1}{\pi}\int^{\infty}_0d\omega\int^{\infty}_{-\infty}f(t)\cos\omega(t-x)dt\]
\end{theorem}

\begin{theorem}[Convolution Theorem]
The convolution of two functions $f$ and $g$ is defined to be \[(f\ast g)(t)=\int^{\infty}_{-\infty}f(\tau)g(t-\tau)d\tau\] The convolution theorem states that \[\widehat{f\ast g}=\hat{f}\hat{g} \text{ and } \widetilde{f\ast g}=\tilde{f}\tilde{g}\]
\end{theorem} 

\subsection{The case of initially zero bunch length}

In this case we have that $\xi(t')=\delta(t')$, so the fast rotation signal becomes \[S(t)=\sum^{\infty}_{n=0}\frac{\rho\left(\frac{t}{(n+\theta/2\pi)T}-1\right)}{(n+\theta/2\pi)T}\]
Assuming the bunch evolves such that in the first turn the beam spreads negligibly, the center of mass of the bunch reaches the fiber harp at position $\theta$ at some time $t_0$. This $t_0$ is the time when muons at the magic frequency first reach the detector. Furthermore, we have that $\theta/2\pi=t_0/T$, so we may write 

\begin{equation}
S(t)=\sum^{\infty}_{n=0}\frac{\rho\left(\frac{t}{nT+t_0}-1\right)}{nT+t_0}
\end{equation}
We next assume that $\mathcal{S}(t)\equiv S(t+t_0)$ is sufficiently well behaved so as to be absolutely integrable on $[0,\infty)$, as well as piecewise continuous and piecewise differentiable. Note that this means that $\rho(\Delta)$ must satisfy these conditions also. Suppose we extend $\mathcal{S}$ to the entire real line as an even function. By Theorem 1, we may express $\mathcal{S}$ as \[\mathcal{S}(t)=\frac{1}{\pi}\int^{\infty}_0d\omega\int^{\infty}_{-\infty}\mathcal{S}(t')\cos\omega(t'-t)dt'\]  But we made $\mathcal{S}$ even, so the expression simplifies to \[\mathcal{S}(t)=\frac{2}{\pi}\int^{\infty}_0\cos\omega td\omega\int^{\infty}_0\mathcal{S}(t')\cos\omega t'dt'\] Since the formula above only considers values of $t\geq0$, we may recover $S(t)$:\[S(t+t_0)=\frac{2}{\pi}\int^{\infty}_0\cos\omega td\omega\int^{\infty}_0S(t'+t_0)\cos\omega t'dt'=\]\[\frac{2}{\pi}\int^{\infty}_0\cos\omega td\omega\int^{\infty}_{t_0}S(t')\cos\omega(t'-t_0)dt'\Rightarrow\]

\begin{equation}
S(t)=\frac{2}{\pi}\int^{\infty}_0\cos\omega(t-t_0)d\omega\int^{\infty}_{t_0}S(t')\cos\omega(t'-t_0)dt'
\end{equation} 
We then have that \[\mathcal{S}(t)=\tilde{\hat{\mathcal{S}}}(t)=\frac{1}{2\pi}\int^{\infty}_{-\infty}e^{-i\omega t}d\omega\int^{\infty}_{-\infty}\mathcal{S}(t')e^{i\omega t'}dt'=\]\[\frac{1}{2\pi}\int^{\infty}_{-\infty}e^{-i\omega t}d\omega\int^{\infty}_{-\infty}\mathcal{S}(t')(\cos\omega t'+i\sin\omega t')dt'=\frac{1}{2\pi}\int^{\infty}_{-\infty}e^{-i\omega t}d\omega\int^{\infty}_{-\infty}\mathcal{S}(t')\cos\omega t'dt'=\] where we used the fact that $\mathcal{S}$ is an even function, and the integral of the product of an even and odd function vanishes. From the preceding expression we now see that $\hat{\mathcal{S}}$ is an even function. So we write \[\frac{1}{2\pi}\int^{\infty}_{-\infty}\hat{\mathcal{S}}(\omega)\cos\omega td\omega=\frac{1}{\pi}\int^{\infty}_0\hat{\mathcal{S}}(\omega)\cos\omega td\omega=\frac{2}{\pi}\int^{\infty}_0\cos\omega td\omega\int^{\infty}_0\mathcal{S}(t')\cos\omega t'dt'\] Thus 

\begin{equation}
\hat{S}(\omega)=\sqrt{\frac{2}{\pi}}\int^{\infty}_{t_0}S(t)\cos\omega(t-t_0)dt
\end{equation} 
is the Fourier transform of $S$. So if we're given $\hat{S}(\omega)$, we may express $S$ as 

\begin{equation}
S(t)=\sqrt{\frac{2}{\pi}}\int^{\infty}_0\hat{S}(\omega)\cos\omega(t-t_0)d\omega=\frac{1}{\sqrt{2\pi}}\int^{\infty}_{-\infty}\hat{S}(\omega)\cos\omega(t-t_0)d\omega
\end{equation}

\subsection{Symmetric Bunch Length Distribution $\xi(t')$}
Consider the fast rotation signal of the previous subsection above; call it $S_0(t)$ for now. We have that given an initial longitudinal distribution $\xi(t')$, \[S(t)=\int\xi(t')S_0(t-t')dt'=(\xi\ast S_0)(t)\] where $\ast$ is the convolution operator. If the support of $\xi$ is $(t_1,t_2)$, then the support of $S(t)$ is $(t_0+t_1,\infty)$ (the support of $S_0(t)$ is $(t_0,\infty)$) Using $(4)$, we have \[S(t)=\frac{2}{\pi}\int\xi(t')dt'\int^{\infty}_0\cos\omega(t-t'-t_0)d\omega\int^{\infty}_{t_0}S_0(\tilde{t})\cos\omega(\tilde{t}-t_0)d\tilde{t}=\]\[\sqrt{\frac{2}{\pi}}\int\xi(t')dt'\int^{\infty}_0\hat{S}_0(\omega)\cos\omega(t-t'-t_0)d\omega=\]\[\sqrt{\frac{2}{\pi}}\int\xi(t')dt'\int^{\infty}_0\hat{S}_0(\omega)(\cos\omega(t-t_0)\cos\omega t'+\sin\omega(t-t_0)\sin\omega t')d\omega=\]\[\sqrt{\frac{2}{\pi}}\int\xi(t')dt'\int^{\infty}_0\hat{S}_0(\omega)\cos\omega(t-t_0)\cos\omega t'd\omega=\]\[\sqrt{\frac{2}{\pi}}\int^{\infty}_0\hat{S}_0(\omega)\langle\cos\omega t'\rangle\cos\omega(t-t_0)d\omega\] where we used parity of sine and $\langle\cos\omega t'\rangle=\int\xi(t')\cos\omega t'dt'$. So we have that...

\subsection{Asymmetric Bunch Length Distribution $\xi(t')$}

\subsection{Physical Interpretation of the Fourier Transform of the Fast Rotation Signal}

Taken directly, the Fourier transform of the fast rotation signal presents the relative amount of different frequency cosines present in the fast rotation signal. But the fast rotation signal is a result of the revolution of muons with frequencies determined by a distribution. This distribution remains fixed in time...
%The established method in~\cite{orlov} for extracting the momentum (or equivalently the frequency or radius distribution) is to take the real part of the Fourier transform of the fast rotation signal. Suppose the center of mass of the muon beam first passes the detector at time $t_0$, and the detector starts detecting at some time $t_s>t_0$.  Let $S(t)$ be the fast rotation signal of a muon beam with Gaussian momentum distribution. Then  %

\section{Analysis for a Gaussian Energy Offset Distribution and Initially Zero Bunch Length}

If the energy offset distribution is a Gaussian with width $\Delta_0$, then \[S(t)=\sum^{\infty}_{n=0}\frac{e^{-(t-(nT+t_0))^2/2\Delta^2_0(nT+t_0)^2}}{\sqrt{2\pi}\Delta_0(nT+t_0)}\] Suppose the center of mass of the muon beam first passes the detector at time $t_0$, and the detector starts detecting at some time $t_s>t_0$. Then the Fourier transform of the fast rotation signal is

\begin{gather}
\hat{S}(\omega)=\int^{\infty}_{t_s}S(t)\cos\omega(t-t_0) dt \nonumber \\
=\sum^{\infty}_{n=0}\int^{\infty}_{t_s}\frac{e^{-(t-(nT+t_0))^2/2\Delta^2_0(nT+t_0)^2}}{\sqrt{2\pi}\Delta_0(nT+t_0)}\cos\omega(t-t_0)dt \nonumber \\ 
=\sum^{\infty}_{n=0}\frac{e^{-1/2\Delta^2_0}}{2\sqrt{2\pi}\Delta_0(nT+t_0)}\int^{\infty}_{t_s}e^{-t^2/2\Delta^2_0(nT+t_0)^2}e^{t/(nT+t_0)\Delta^2_0}e^{\pm i\omega t}e^{\mp i\omega t_0}dt.
\end{gather}
From Gradshteyn and Rizhik [??ref??], we know that 
\begin{equation}
\int^{\infty}_u\exp\left(-\frac{x^2}{4\beta}-\gamma x\right)dx=\sqrt{\pi\beta}e^{\beta\gamma^2}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left(\gamma\sqrt{\beta}+\frac{u}{2\sqrt{\beta}}\right)\right),
\end{equation}
for $\text{Re}(\beta)>0$ and $u\geq0$. Thus the result of using this integral in computing the Fourier transform is $\hat{S}(\omega)=$ 

\begin{gather}
\sum^{\infty}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}-\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)+ \nonumber \\
\sum^{\infty}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{-i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}+\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right).
\end{gather}

Something to note about Eq.~\ref{eq:??}NEED TO REFERENCE LABEL, NO HARD-CODED REFERENCe  
is that if we start the sum from say, index $j-1$, then the first $j-1$ spikes of the signal, 
corresponding to the detector seeing the beam the first $j-1$ turns, will disappear. 
So the observed signal may be written as 
\[\sum^{\infty}_{n=j}\frac{\exp[-(t-(nT+t_0))^2/2\Delta^2_0(nT+t_0)^2T^2]}{\sqrt{2\pi}\Delta_0(nT+t_0)T}\]. 
Reindexing the sum gives us 

\begin{equation}
\sum^{\infty}_{n=0}\frac{\exp[-(t-((n+j)T+t_0))^2/2\Delta^2_0((n+j)T+t_0)^2T^2]}{\sqrt{2\pi}\Delta_0((n+j)T+t_0)T}
\end{equation}

Given $t_s$, $t_0$, and $T$, the corresponding starting index in the expression for $S(t)$ is $m=\lceil{(t_s-t_0)/T}\rceil$. Hence the immediately observed frequency spectrum can also be expressed as $\hat{S}(\omega)=$ 

\begin{gather}
\sum^{\infty}_{n=m}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}-\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)+ \nonumber \\
\sum^{\infty}_{n=m}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{-i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}+\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)
\end{gather}

\subsection{Corrections to the Fourier transform} The detector in the section above started to detect the muon beam at a time $t_s>t_0$. In the time that the detector does not detect the beam, some decoherence of the fast rotation signal occurs, resulting in lost frequency content in the Fourier transform above. This results in distortions of the frequency spectrum.  Consider the integral of $S(t)$ between times $t_0$ and $t_s$: 
\begin{equation}
\Delta(\omega)=\int^{t_s}_{t_0}S(t)\cos\omega(t-t_0)dt
\end{equation}

This is the part of the frequency spectrum that the detector fails to account for. Let's take a closer look at $\Delta$. \[\Delta(\omega)=\int^{t_s}_{t_0}S(t)\cos\omega(t-t_0)dt\]\[=\int^{\infty}_{t_0}S(t)\cos\omega(t-t_0)dt-\int^{\infty}_{t_s}S(t)\cos\omega(t-t_0)dt\] Using the integral given in Gradshteyn and Ryzhik, we have 

\begin{gather}
\sum^{\infty}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}-\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_0}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)+ \nonumber \\
\sum^{\infty}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{-i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}+\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_0}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right) \nonumber \\
-\sum^{\infty}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}-\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)+ \nonumber \\
-\sum^{\infty}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{-i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}+\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)
\end{gather}

But keeping in mind the reasoning leading to $(8)$ and $(9)$, we may instead write $\Delta(\omega)=$
\begin{gather}
\sum^{m-1}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}-\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_0}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)\nonumber+\\ 
\sum^{m-1}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{-i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}+\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_0}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)\nonumber \\
-\sum^{m-1}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}-\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)\nonumber \\ 
-\sum^{m-1}_{n=0}\frac{e^{-\omega^2(nT+t_0)^2\Delta^2_0/2}e^{-i\omega nT}}{4}\left(1-\frac{\sqrt{\pi}}{2}\text{Erf}\left[\frac{-1}{\Delta_0\sqrt{2}}+\frac{i\omega (nT+t_0)\Delta_0}{\sqrt{2}}+\frac{t_s}{\Delta_0(nT+t_0)\sqrt{2}}\right]\right)
\end{gather}

In the vicinity of the magic frequency, $\Delta$ is expected to be parabolic. Looking at the figures below, we can see that this is indeed true.

\subsection{Investigation of the Established Method for Extracting $\Delta$}

The established method for extracting $\Delta$ asserts that we may extract it by using $\hat{S}(\omega)$. We have that  \[\Delta(\omega)=\int^{t_s}_{t_0}S(t)\cos\omega(t-t_0)dt\] The idea is that although we do not observe $S(t)$ for times $t_0<t<t_s$, we may reasonably approximate $S(t)$ on this interval of time:\[S(t)=\int \hat{S}(f')\cos2\pi f'(t-t_0)df'\] Substituting this expression for $S(t)$ into the integral for $\Delta$, we have \[\Delta(f)=\iint^{t_s}_{t_0}\hat{S}(f')\cos2\pi f'(t-t_0)\cos2\pi f(t-t_0)dtdf'=\]\[\frac{A}{2\pi^2}\int \hat{S}(f')\left(\frac{\sin2\pi(f-f')(t_s-t_0)}{f-f'}+\frac{\sin2\pi(f+f')(t_s-t_0)}{f+f'}\right)df'\] We may ignore the second term in the parentheses as their contribution is negligible. Thus \[\Delta(f,t_s)=\frac{A}{2\pi^2}\int \hat{S}(f')\frac{\sin2\pi(f-f')(t_s-t_0)}{f-f'}df'\]


The established method for extracting $\Delta$ asserts that we may get \[\Delta(\omega)=2\pi(t_s-t_0)\int^{\infty}_{-\infty}\hat{S}(\omega')\frac{\sin(\omega-\omega')(t_s-t_0)}{(\omega-\omega')(t_s-t_0)}d\omega'\] where $\hat{S}(\omega')$ is the frequency distribution extracted from the immediate detector data, with no corrections applied. For small $\omega-\omega')(t_s-t_0)$, we may approximate the integral using the fact that $\text{sinc}(x)=1-x^2/6$ for $x<<1$. Then \[\Delta(\omega)\approx2\pi(t_s-t_0)\int^{\infty}_{-\infty}\hat{S}(\omega')\left(1-\frac{(\omega-\omega')^2(t_s-t_0)^2}{6}\right)d\omega'\]\[=2\pi(t_s-t_0)\int^{\infty}_{-\infty}\hat{S}(\omega')d\omega'-\frac{2\pi(t_s-t_0)^3}{6}\int^{\infty}_{-\infty}\hat{S}(\omega')(\omega^2-2\omega\omega'+\omega'^2)d\omega'\]
